\documentclass[10pt,twoside,twocolumn]{article}

\begin{document}
\title{Real-time Data Analytics}
\author{Hard-working authors\\
Chair of Sociology, in particular Modeling and Simulation\\
ETH Zurich, Zurich, Switzerland
}
\date{\today}
\maketitle

\section{Introduction}

Motivation of this survey paper~\cite{Hatamlou2014}

\section{Fundamentals on Data Analytics}

Here we give definitions and background on data analytics in general. 

- e.g. what analytics types do we have? in-network aggregation, data queries etc. 

\section{Real-time Data Analytics}

Here we illustrate the aspects of real-time data analytics. 

- Which aspects does it involve? data mining, visualization, streaming etc.

- Some nice picture with the concepts will be useful for the rest of the paper.

\section{Emergent Applications}

We review and illustrate emergent applications of real-time data analytics.

- Which requirements qualify an application for real-time data analytics? (a comparison table here would be nice)

\section{Data}

Data types/semantics and their role in real-time data analytics, e.g. textual, numerical, meta-data?

\section{Methods and Techniques}

Illustration of methods, e.g. clustering, Bayes networks, etc.

- Comparison in different dimensions, e.g. performance, privacy, centralized vs. decentralized, etc.

\section{Architectures}

Complete architectures, applicability and design choices.

\section{Technologies}

Technologies for implementing real-time data analytics

\section{Policies and Societal Impact}

What policies exist for real-time data analytics
	
- What controversies, influence and impact real-time data analytics introduce in our society?

\section{Guidelines for Researchers and Practitioners}

It is nice to have some guidelines for researchers and practitioners about what we learn from all these.

\section{Open Research Questions}

We should guide and motivate other researchers to do future work.

\section{Conclusions}

The grant conclusions of this survey. 

\bibliography{survey-analytics} 
\bibliographystyle{abbrv}

\end{document}